Test of Adaptable User Interfaces

### 2015-07-08 paper.tex
First part of the case study section

% =============================================================================
\section{Related Work}
% =============================================================================
With the popularity of Continuous Integration (CI), a software engineering practice in which isolated changes are immediately tested and reported on when they are added to a larger code base, the need of test automation increased. Test automation can be analyzed in three ways: the generation of test scripts, the execution of tests and the analysis of the test results. The scientific community has developed several approaches and tools for automation of regular and UI testing. Some of them will be presented below.

An example of automation for the generation of test script is Tobias~\cite{tobias}, a combinatorial tool that instantiates a large set of test sequences from an abstract description. Combinatorial testing allows to express a large set of test cases in a few lines. Tobias receives the abstractly written tests and generates an executable test code containing several possible combinations of execution, according to the specification of the abstract entry code.

In the case of execution automation, several tools have been developed focusing on UI testing. They are tools that drive the UI as users do, triggering actions, navigating the system and checking the UI content. For instance, tools for web~\cite{watir, cucumber} and mobile~\cite{appium, selendroid} environments are responsible for interacting with the UI according to the scripts written by the testers. Besides, there are tools~\cite{selenium, monkeytalk} that are also able to generate test scripts, through the process of record and playback. The user interacts with the system, the tool records the actions generating a testing script that can be user for execution automation.

Other interesting approach, proposed in~\cite{test-image-comparison-korea}, uses the idea of record and playblack with the automation of the analysis of the results through image comparison. In this solution, after the execution of a test script, the image of the UI is recorded. It can be used later to verify if changes in the system affected the UI, comparing automatically the old and new images of the UI.

Another related work, presented in~\cite{ui-equilavance-raquel}, is not about testing, but comparing UIs of the same system that are adapted to different contexts. In this approach, the UIs are abstracted to formal models based on graphs and the abstracts can be automatically compared, verifying if  they have the same capabilities and appearance.

% =============================================================================
\section{Case Study}
% =============================================================================
TODO

>>>>

% =============================================================================
\section{Related Work}
% =============================================================================
TODO

% =============================================================================
\section{Case Study}
The case study used in this work is a prototype for a smart home energy management system. This decision is based on the fact that it is a modern concept, little explored in the domain of this research and whose UIs can be adapted to several contexts. A smart home may be defined as a well-designed structure with sufficient access to assets, communication, controls, data, and information technologies for enhancing the occupants' quality of life through comfort, convenience, reduced costs and increased connectivity~\cite{smart-home-harper}. A smart home energy management system is an energy management system applied to smart homes. It allows users to control and monitor the energy consumption in a residence from different devices.

It is a prototype because we have developed only the UIs of the system for four versions, three for web environment and one as a mobile application. The data of the system are predetermined. All versions have the same features, except for two web versions that have an additional feature. The differences between the versions are visual. In the case of the mobile application, the UI is adapted to a mobile device, which contains a smaller screen and its own platform for UI development. In the case of the web versions, the UIs have also been developed to this context, using web UI technologies. But the differences between the three web versions are changes in the navigation and UI components. In this paper, we focus on the following features of the prototype:

\begin{enumerate}

\item \textbf{Goal}: the user can check information about the general energy consumption per month. Having access to the goal and consumption in kWh for the chosen month.

\item \textbf{Filter}: the user has access to a list of all his or her objects in the house, having the possibility to filter this list per room. An object means any component that can be controlled and whose energy consumption can be registered, such as lights and electronic devices.

\item \textbf{Comparator}: the user can choose two objects and compare, side by side, their energy consumption charts. This feature is present in only two of the web versions.

\end{enumerate}
